### 2013-11-10 research/MCR report/main.tex
uploaded 22-oct 2013 6.36
uploaded 10-11-2013 2.03 pm

\documentclass{article}  
\usepackage{a4wide}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{tabulary}
\usepackage[sort]{cite}
%\usepackage[sort,nocompress]{cite}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{placeins}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{pdfpages}
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}

@@

@@

\begin{itemize}
\item   the system is not frequency dependent, but more dependent on the velocity amplitude.
\item The main tuning parameter on the mechanical system to obtain an optimum power output is the damping factor.
\end{itemize}

@@

In order to carry out an optimisation study on the fluid dynamics portion of the system, it is essential to study underlying fluid mechanics for galloping. It has been already established by \cite{Parkinson1964} that the instantaneous lift is the input of the system. Therefore it is essential to have an understanding on how exactly this lift occur. According to \cite{Parkinson1989},\hilight{Luo 94} the lift force is crated by the secondary flow of the two shear layers of either side of the body which creates an unbalanced pressure distribution on the afterbody. If a square cross section is taken as an example, when the body have a transverse $\dot{y}$, the relative velocity causes an instantaneous angle of attack which makes one shear layer lies closer to the body than the other. Therefore the shear layer near the body creates a pressure imbalance by creating a higher suction on the wall of the body on the adjacent side than the suction caused by the shear layer on the opposite side on its adjacent side of the body. The lift force become its maximum when the shear layer closer to the body re attaches at the trailing edge. As the angle of attack is further increased, the separated shear layer in the opposite side of the body (which was initially away from the body) shrinks therefore the pressure difference decreases which results a decrease in the lift force. This explanation was validated by \cite{Luo1994} by conducting flow visualisation experimentally.

@@

%\section{Difficulties and challenges} 
%%
%%\begin{enumerate}
%%      
%%\end{enumerate}
%\bibliographystyle{elsarticle-harv}
%\bibliography{../bibtex/MCR}
%\appendix
%%\begin{center}
%%\section*{\LARGE Appendix 1}
%%\addcontentsline{toc}{section}{Appendix 1} 
%%\end{center}
Proposed table of contents of the final PhD thesis:
\begin{enumerate}
\item Preliminary remarks 
\item A review of literature
\begin{enumerate}[i]
\item Introduction
\item Flow induced vibrations 
\item Flow induced vibrations as a mechanism of energy harvesting
\item Aeroelastic galloping
\item Behaviour of shear layer 
\end{enumerate}
\item Methodology and validation
\begin{enumerate}[i]
\item Introduction
\item Governing equations and quasi-steady state model 
\item Numerical methods and boundary conditions 
\item The governing equations for the DNS method: Naiver-Stokes and continuity  
\item Discretisation  
\item Integration of substep equation 
\item Boundary conditions 
\item Spectral element method
\item Convergence and validation studies 
\item Summary
\end{enumerate}
\item Galloping response and natural frequency
\begin{enumerate}[i]
\item Introduction
\item

\end{enumerate}
\item Effect of mechanical parameters on power output
\begin{enumerate}[i]
\item Introduction
\item Natural frequency 
\item Damping constant 
\item Mass ratio
%\item Sleep mode enabled core network
\item Summary
\end{enumerate}
\item{Optimisation of the cross sectional shape for a better power output}
\item{FSI validation}
\item Conclusion
%\begin{enumerate}[i]
%\item Introduction
%\item Summary of the work
%\item Future directions
%\end{enumerate}
\end{enumerate}
%Each sub-section mentioned above could be further divided into sections, if necessary. For example, 3(v) could be divided as 3(v)(a) "ILP formulation", 3(v)(b) "Heuristic algorithm" and 3(v)(c) "Evaluation"
%\newpage
%\centering
%\vspace*{2.5in}

>>>>

\documentclass{article}  
\usepackage{a4wide}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{tabulary}
%\usepackage[sort]{cite}
%\usepackage[sort,nocompress]{cite}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{placeins}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{epstopdf}
\usepackage{enumerate}
\usepackage{pdfpages}
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}

@@

\begin{itemize}
\item To understand the underpinning mechanical parameters of the system and find methods to optimize it to obtain a higher power output 
\item To understand the governing fluid mechanics of a system under aeroelastic galloping 
\item To identify methods to manipulate and control the fluid mechanics to obtain a better power output.  
\end{itemize}

@@

\begin{itemize}
\item   The system is not frequency dependent, but more dependent on the velocity amplitude.
\item The main tuning parameter on the mechanical system to obtain an optimum power output is the damping factor.
\item An effect of the mass ratio could be observed as the mass ratio reduces for both higher and lower Reynolds numbers. 
\end{itemize}

@@

In order to carry out an optimisation study on the fluid dynamics portion of the system, it is essential to study underlying fluid mechanics for galloping. It has been already established by \cite{Parkinson1964} that the instantaneous lift is the input of the system. Therefore it is essential to have an understanding on how exactly this lift occur. According to \cite{Parkinson1989},\hilight{Luo 94} the lift force is created by the secondary flow of the two shear layers of either side of the body which creates an unbalanced pressure distribution on the afterbody. If a square cross section is taken as an example, when the body have a transverse $\dot{y}$, the relative velocity causes an instantaneous angle of attack which makes one shear layer lies closer to the body than the other. Therefore the shear layer near the body creates a pressure imbalance by creating a higher suction on the wall of the body on the adjacent side than the suction caused by the shear layer on the opposite side on its adjacent side of the body. The lift force become its maximum when the shear layer closer to the body re attaches at the trailing edge. As the angle of attack is further increased, the separated shear layer in the opposite side of the body (which was initially away from the body) shrinks therefore the pressure difference decreases which results a decrease in the lift force. This explanation was validated by \cite{Luo1994} by conducting flow visualisation experimentally.

@@

%\section{Difficulties and challenges} 
%%
%%\begin{enumerate}
%%      
%%\end{enumerate}
%\bibliographystyle{elsarticle-harv}
%\bibliography{../bibtex/MCR}
%\appendix
%%\begin{center}
%%\section*{\LARGE Appendix 1}
%%\addcontentsline{toc}{section}{Appendix 1} 
%%\end{center}
Proposed table of contents of the final PhD thesis:
\begin{enumerate}
\item Preliminary remarks 
\item A review of literature
\begin{enumerate}[i]
\item Introduction
\item Flow induced vibrations 
\item Flow induced vibrations as a mechanism of energy harvesting
\item Aeroelastic galloping
\item Behaviour of shear layer 
\end{enumerate}
\item Methodology and validation
\begin{enumerate}[i]
\item Introduction
\item Governing equations and quasi-steady state model 
\item Numerical methods and boundary conditions 
\item The governing equations for the DNS method: Naiver-Stokes and continuity  
\item Discretisation  
\item Integration of substep equation 
\item Boundary conditions 
\item Spectral element method
\item Convergence and validation studies 
\item Summary
\end{enumerate}
\item Power analysis for high and low Reynolds numbers
\begin{enumerate}[i]
\item Introduction 
\item Stationary data 
\item Natural frequency 
\item Damping constant 
\item Mass ratio
\item Summary 
\end{enumerate}

\item Optimisation of the cross sectional shape 
\item FSI validation
\item Conclusion
%\begin{enumerate}[i]
%\item Introduction
%\item Summary of the work
%\item Future directions
%\end{enumerate}
\end{enumerate}

### 2013-11-10 research/paper/figure/time_history_msar_mass.tex
uploaded 10-11-2013 2.03 pm

  \caption{ Time histories of velocity. Data presented at \reynoldsnumber=22300, \ustar=175 and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$ at three different mass ratios: (a) $m^*=1164$, (b) $m^*=10$ and (a) $m^*=5$. As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal as a result of reduction of frequency.}

>>>>

  \caption{ Time histories of displacement and velocity at \reynoldsnumber=22300, \ustar=175 and $\frac{c}{\rho\mathcal{A}U}=9.3\times10^{-1}$. The velocity time histories are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$. The time history of displacement are presented for: (a) $m^*=1164$; (b) $m^*=10$; (c) $m^*=5$   As the mass ratio decreases the signal tend to transform from a sinusoidal towards a square signal and the displacement signal tend to move towards a triangular signal due to reduction in inertia.}
